Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing text changes to intro in paper.qmd

The analysis, modeling, and visualizations of this paper were conducted using the programming language `R` [@citeR] and the following packages: `tidyverse` @Tidyverse , `janitor` @Janitor for data cleaning, `kableExtra`@kableExtra for dynamic report generation and table formatting, `modelsummary` @Modelsummary for summarizing models, `usmap` @usmap for mapping U.S. states, `arrow` @arrow for data integration with Apache Arrow, `lubridate` @Lubridate for date handling, `rstanarm` @rstanarm and `brms` @brms for Bayesian regression modeling, `Matrix` @Matrix for handling sparse and dense matrices, `splines` @splines for regression splines, `caret` @caret for machine learning support, and `broom.mixed`  @broommixed for tidying mixed models.

>>>>

The analysis, modeling, and visualizations of this paper were conducted using the programming language `R` [@citeR] and the following packages: `tidyverse` package of @Tidyverse , `janitor` package of @Janitor for data cleaning, `kableExtra` package of @kableExtra for dynamic report generation and table formatting, `modelsummary` package of @Modelsummary for summarizing models, `usmap` package of @usmap for mapping U.S. states, `arrow` package of @arrow for data integration with Apache Arrow, `lubridate` package of @Lubridate for date handling, `rstanarm` package of @rstanarm and `brms` package of @brms for Bayesian regression modeling, `Matrix` package of @Matrix for handling sparse and dense matrices, `splines` package of @splines for regression splines, `caret`package of @caret for machine learning support, and `broom.mixed` package of @broommixed for tidying mixed models.
